Lattice Boltzmann simulations of magnetically responsive\\ anisotropic particle stabilized emulsions

### 2025-02-20 chapters/LBM_technique.tex
Changes 1. Added more analysis to application of magnetic fields during formation chapter 2. Added references to fix some (not all) literature reference issues 3. Added some detail in analysis techniques section
Changes 1. Modify method section to flow better

This work uses a multicomponent Lattice Boltzmann Method (LBM) to simulate the hydrodynamics of two partially miscible, 
incompressible fluids as implemented in LB3D. The LBM solves the Navier-Stokes equation at the incompressible limit, 
$\rho \frac{d \overrightarrow{u}}{dt} = \eta \Delta \overrightarrow{u} + \frac{\nabla P}{\rho} + F_{body}$, at low 
Mach and Reynolds numbers, incorporating density $(\rho)$, viscosity $(\eta)$, velocity $(u)$, pressure $(P)$, and 
body force $(F_{body})$. \cite{qian_lattice_1992, chin_lattice_2002, nourgaliev_lattice_2003} The Shan-Chen pseudopotential
model is used to simulate the Cahn-Hilliard equation, $\frac{d c^k}{dt} = M^k\Delta \mu - \nabla u^k c^k$, for the non-ideal 
mixture model. \cite{shan_lattice_1993, shan_simulation_1994, he_lattice_1997, he_discrete_1998} $c^k$, $M^k$ and $u^k$ is the 
concentration, mobility and velocity of species $k$ respectively while $\mu$ is the free energy of system. Particle dynamics 
include Hertzian contact and lubrication forces, tracked with classical Newtonian mechanics, while particle-fluid coupling 
involves momentum exchange to simulate viscous dissipation. Particle-particle magnetic interactions are modeled using dipole 
interactions. \cite{davies_interface_2014, xie_direct_2017, xie_controllable_2021} A more detailed description of the model is 
provided in the following sections

\section{Hydrodynamics}

@@

The BGK operator limits simulations to low reynolds number and mach numbers to prevent numerical instabilities. 
\cite{qian_lattice_1992} The kinematic viscosity if using the BGK operator is defined as 
$\nu = c_s^2(\tau - \frac{\Delta t}{2})$. The equilibrium distribution is obtained from a discretized expansion of the 
Maxwell-Boltzmann distribution to the second order. \cite{he_theory_1997, succi_lattice_2018} This is shown in equation 
\ref{eq:LBM_Feq}.

\begin{equation}
    f_{i}^{eq}(\mathbf{x}, t) = w_i\rho(1 + \frac{\mathbf{c_i} \cdot \mathbf{u}}{c_s^2} + \frac{(\mathbf{c_i} \cdot 
    \mathbf{u})^2}{2c_s^4} + \frac{\mathbf{u} \cdot \mathbf{u}}{2c_s^2} + \frac{(\mathbf{c_i} \cdot 
    \mathbf{u})^3}{6c_s^6} - \frac{(\mathbf{c_i} \cdot \mathbf{u})\mathbf{u}^2}{4c_s^3})
    \label{eq:LBM_Feq}
\end{equation}

@@

$\rho$ and $\textbf{u}$ in Equation \ref{eq:LBM_Feq} are defined as the macroscopic parameters for density and velocity 
and can be calculated from the mass distribution using $\rho = \sum f_i$ and $\rho \mathbf{u} = \sum f_i \mathbf{c}_i$ 
respectively. Using the Chapman-Enskog expansion, the Navier-Stokes equation at the incompressible limit at low-reynolds 
numbers can be recovered. \cite{qian_lattice_1992, he_lattice_1997} The regime accessible through this method is suitable 
for simulations in this work as the $ 1 \leq Re \leq 100 $ and the mach number, $Ma < 0.01$, fulfilling the stability 
criterion and usage requirements for the presented hydrodynamic model.

\section{Non-ideal mixing}

@@

\begin{equation}
F_{k}^{SC}(\mathbf{x}, t) = -\Psi^{k}(\mathbf{x}, t)\sum_{k'}g_{cc'}\sum_{\mathbf{x'}}\Psi_{k'}(\mathbf{x'}, t)(\mathbf{x'} 
- \mathbf{x})
\label{eq:sc_model}
\end{equation}

An effective mass of each fluid at node $\mathbf{x}$ is used in place of the actual density to scale it between zero 
and one and is defined as $\psi^{c}(\mathbf{x},t) = \rho_{0}\left[1 - \exp(-\frac{\rho^{k}(\mathbf{x}, t)}{\rho_{0}})\right]$. 
In this model, the SC force is incorporated into the macroscopic velocities written as 
$\mathbf{u}_k =  \mathbf{u}_k + \frac{\tau}{\rho} F_{k}$ and finally the equilibrium distribution of each fluid species.

\section{Suspended particle dynamics}

Suspended particles will be coupled to the LB fluid based on the work conducted by Ladd. \cite{ladd_numerical_1994, 
aidun_direct_1998, ladd_lattice-boltzmann_2001} The particles follow Newtonian mechanics with force 
$\mathbf{F_p} = m_p\frac{d \mathbf{u_p} }{dt}$ and rotational inertia $\mathbf{D_p} = J_p \frac{d \mathbf{\omega_{p}}}{dt}$. 
$\mathbf{F_p}$ and $\mathbf{D_p}$ represent the force and torque acting on a particle with mass $m_p$ and moment of inertia 
$J_p$. $\mathbf{u}_p$ and $\mathbf{\omega_{p}}$ are the linear and angular velocities of the particle. The equations of 
motion are evolved over time using a leapfrog integrator. \cite{jansen_bijels_2011}

The particles are discretized on the lattice according to the method laid out in Ladd and Aidun 
\cite{ladd_lattice-boltzmann_2001}. Coupling to the LB fluid is done through momentum exchange with the 
fluid through modification of the velocity surrounding the fluid. The discretized particles have a no-slip 
boundary condition implemented as a modified bounce back boundary condition, with momentum exchange between 
particle and fluid done by changing the post collision population distribution, $f^{*}_{i}(\mathbf{x}, t)$, 
shown in Eq \ref{eq:md_LBM_mod}

\begin{equation}
    f^{*}_{i'}(\mathbf{x}, t + \Delta t) = f^{*}_{i}(\mathbf{x}, t) - \frac{2 w_{i}}{c_s^2}\rho^k \mathbf{u}_{surf} 
    \cdot \mathbf{c_i}
    \label{eq:md_LBM_mod}
\end{equation}

In this work, $i'$ is defined such that $\mathbf{c_i} = -\mathbf{c_{i'}}$ to satisfy the bounce-back boundary condition. 
The fluid velocity at the particle surface, $\mathbf{u}_{surf}$, is the sum of the particle's linear and rotational 
velocities, $\mathbf{u}_{surf} = \mathbf{u_p} + R_i\mathbf{\omega_p}$. Advection of populations occurs after this exchange. 
The total force and torque on the particle are calculated by summing the total momentum over its surface. As particles 
move, they cover and uncover fluid grid points. Covered points are removed, while the composition of newly uncovered 
points in a multiphase fluid is averaged from adjacent grid points.

\subsection{Anisotropic particles}

Under 1 lattice unit additional lubrication forces are required to reduce the likelihood of particle overlap. For 
spherical particles, this is defined in Equation \ref{eq:sphere_lube}

\begin{equation}
    \mathbf{F}_l = -6\pi \eta \frac{R_{i}^{2} R_{j}^{2}}{(R_i + R_j)^2}(\frac{1}{|\mathbf{r}_{ij}| -R_i - R_j} -\frac{1}{\Delta_c}) \frac{(\mathbf{u}_{ij}\cdot\mathbf{r}_{ij})\mathbf{r}_{ij}}{|\mathbf{r}_{ij}|^2}
    \label{eq:sphere_lube}
\end{equation}

where $R_i$ and $R_j$ are the radii of each particle involved in the interaction, $\mathbf{r}_{ij}$ is the distance
 vector between the particle centers, $\mathbf{u}_{ij}$ are the relative velocities of the particles and $\Delta_c$ 
 is the cutoff distance when the lubrication force begins to act. A hertzian contact force is also added to ensure 
 that there is no particle overlap, defined in Equation \ref{eq:hertz_def}

\begin{equation}
    \phi_{H} = K_{H}(R_i + R_j - |\mathbf{r}_{ij}|)^{5/2}, r < R_i + R_j
    \label{eq:hertz_def}
\end{equation}

$K_H$ is the force constant used to push particles apart. To correct for the anisotropic particles used in this work, 
the formulas presented in Eqs \ref{eq:sphere_lube} and \ref{eq:hertz_def} can be generalized using the route followed 
in Gunther et al. and Davies et al., inspired by Berne and Pechukas. \cite{gunther_timescales_2014, davies_interface_2014} 
They first begin by rewriting the lubrication and Hertzian contact forces in a dimensionless form below

\begin{equation}
    \phi_{H}(\hat{\mathbf{o_i}}, \hat{\mathbf{o_j}}, \hat{\mathbf{r_{ij}}}) = \epsilon(\hat{\mathbf{o_i}}, 
    \hat{\mathbf{o_j}})\Bar{\phi_{H}}\left( \frac{r_{ij}}{\sigma(\hat{\mathbf{o_i}}, \hat{\mathbf{o_j}}, 
    \hat{\mathbf{r_{ij}}})} \right)
    \label{eq:hertz_anisotropic}
\end{equation}

Equation \ref{eq:hertz_anisotropic} defines the generalization of the Hertz force to allow simulation of ellipsoidal 
particles inspired by Berne and Pechukas. First, the hertzian force is made a function of orientation through the 
addition of eccentricity, $\chi = \frac{R_p^2 - R_o^2}{R_p^2 + R_o^2}$ and an orientation dependent forces, where 
$\epsilon(\hat{\mathbf{o_i}}, \hat{\mathbf{o_j}}) = \frac{\Bar{\epsilon}}{\sqrt{1 - \chi(\hat{\mathbf{o_i}}, 
\hat{\mathbf{o_j}})^2}}$, and $\sigma = \frac{\Bar{\sigma}}{\sqrt{1 - \frac{\chi}{2}( 
\frac{(\hat{\mathbf{r_{ij}}}\hat{\mathbf{o_i}} +  \hat{\mathbf{r_{ij}}}\hat{\mathbf{o_j}})^2}{1 + 
\chi \hat{\mathbf{o_i}}\hat{\mathbf{o_j}}} +  \frac{(\hat{\mathbf{r_{ij}}}\hat{\mathbf{o_i}} -  
\hat{\mathbf{r_{ij}}}\hat{\mathbf{o_j}})^2}{1 - \chi \hat{\mathbf{o_i}}\hat{\mathbf{o_j}}})}}$, 
$\Bar{\sigma} = 2R_{\perp}$. \cite{gunther_lattice_2013, gunther_timescales_2014, davies_assembling_2014}

A similar generalization process is done for the lubrication force, resulting in Equation \ref{eq:md_force} where 
$\mathbf{\Bar{F}}(r) = \hat{\mathbf{r_{ij}}}(\hat{\mathbf{r_{ij}}}(\mathbf{u}_i - \mathbf{u}_j))\left( \frac{1}{r - 1} - 
\frac{\sigma}{\Delta_{c}} \right)$.

\begin{equation}
    \mathbf{F_{ij}}(\hat{\mathbf{o_i}}, \hat{\mathbf{o_j}}, \hat{\mathbf{r_{ij}}}) = \epsilon(\hat{\mathbf{o_i}}, 
    \hat{\mathbf{o_j}})\mathbf{\mathbf{F_{ij}}}\left( \frac{r_{ij}}{\sigma(\hat{\mathbf{o_i}}, \hat{\mathbf{o_j}}, 
    \hat{\mathbf{r_{ij}}})} \right)
    \label{eq:md_force}
\end{equation}

\subsection{Magnetic field and particle coupling}

>>>>

\label{section:methods}

This work uses a multicomponent Lattice Boltzmann Method (LBM) to simulate the hydrodynamics of two partially miscible, 
incompressible fluids as implemented in LB3D. The LBM solves the continuity and Navier-Stokes equation at low
Mach and Reynolds numbers for the fluid, defined as,

\begin{equation}
    \begin{split}
    \frac{\partial\rho}{\partial t} + \nabla\cdot\left(\rho\vec{u}\right) &= 0 , \\
    \frac{\partial\vec{u}}{\partial t} + (\vec{u}\cdot\nabla)\vec{u} &= - \frac{1}{\rho} \nabla p + \nu \nabla^2 \vec{u} ,
    \end{split}
\end{equation}

incorporating density $(\rho)$, viscosity $(\eta)$, velocity $(u)$, pressure $(P)$, and 
body force $(F_{body})$. \cite{qian_lattice_1992, chin_lattice_2002, nourgaliev_lattice_2003} The Shan-Chen pseudopotential
model is used to simulate the Cahn-Hilliard equation, defined below

\begin{equation}
    \begin{split}
    \frac{\partial\phi}{\partial t}+\nabla\cdot\left(\phi\vec{u}\right) &= \nabla \cdot \left( \Gamma  \nabla\phi \right)
    \end{split}
\end{equation}

where $c^k$, $M^k$ and $u^k$ is the concentration, mobility and velocity of species $k$ respectively while $\mu$ is the free energy of system. 
\cite{shan_lattice_1993, shan_simulation_1994, he_lattice_1997, he_discrete_1998}

Particle dynamics include Hertzian contact and lubrication forces, tracked with classical Newtonian mechanics, while 
particle-fluid coupling involves momentum exchange to simulate viscous dissipation. Particle-particle magnetic interactions are modeled using dipole 
interactions. \cite{davies_interface_2014, xie_direct_2017, xie_controllable_2021} A more detailed description of the model is 
provided in the following sections

\section{Hydrodynamics} 
\label{section:lbm_hydrodynamics}

@@

The BGK operator limits simulations to low reynolds number and mach numbers to prevent numerical instabilities. 
\cite{qian_lattice_1992} The kinematic viscosity if using the BGK operator is defined as 
$\nu = c_s^2(\tau - \frac{\Delta t}{2})$. The equilibrium distribution is obtained from a taylor expansion of the 
Maxwell-Boltzmann distribution to the second order. \cite{he_theory_1997, succi_lattice_2018} This is shown in equation 
\ref{eq:LBM_Feq}.

\begin{equation}
    f_{i}^{eq}(\mathbf{x}, t) = w_i\rho(1 + \frac{\mathbf{c_i} \cdot \mathbf{u}}{c_s^2} + \frac{(\mathbf{c_i} \cdot 
    \mathbf{u})^2}{2c_s^4} + \frac{\mathbf{u} \cdot \mathbf{u}}{2c_s^2})
    \label{eq:LBM_Feq}
\end{equation}

@@

$\rho$ and $\textbf{u}$ in Equation \ref{eq:LBM_Feq} are defined as the macroscopic parameters for density and velocity 
and can be calculated from the mass distribution using $\rho = \sum f_i$ and $\rho \mathbf{u} = \sum f_i \mathbf{c}_i$ 
respectively. Using the Chapman-Enskog expansion, the Navier-Stokes equation at the incompressible limit at low mach
numbers can be recovered. \cite{qian_lattice_1992, he_lattice_1997} The regime accessible through this method is suitable 
for simulations in this work as the $ 1 \leq Re \leq 100 $ and the mach number, $Ma < 0.01$, fulfilling the stability 
criterion and usage requirements for the presented hydrodynamic model.

\section{Non-ideal mixing}
\label{section:lbm_non_ideal_mixing}

@@

\begin{equation}
% F_{k}^{SC}(\mathbf{x}, t) = -\Psi^{k}(\mathbf{x}, t)\sum_{k'}g_{cc'}\sum_{\mathbf{x'}}\Psi_{k'}(\mathbf{x'}, t)(\mathbf{x'} 
% - \mathbf{x})
\vec{F}_k(\vec{x}) \Delta t = - \sum_{k'} \sum_i \frac{w_i}{c_s^2} g_{kk'} \psi_k(\vec{x})\psi_{k'}(\vec{x}+\vec{c}_i) \vec{c}_i
\label{eq:sc_model}
\end{equation}

An effective mass of each fluid at node $\mathbf{x}$ is used in place of the actual density to scale it between zero 
and one and is defined as $\psi^{k}(\mathbf{x},t) = \rho_{0}\left[1 - \exp(-\frac{\rho^{k}(\mathbf{x}, t)}{\rho_{0}})\right]$. 
In this model, the SC force is incorporated into the macroscopic velocities that are then used to calculate the equilibrium
distribution $f_{i}^{k, eq}$ for fluid $k$, defined as,

\begin{equation}
\vec{u}_k^{\text{eq}} = \vec{u}' + \frac{\tau_k}{\rho_k} \vec{F}_k
\end{equation}

Where $\vec{u}'$ is defined as the common grid velocity and is calculated from $f_i^k$ below

\begin{equation}
    \sum_k \frac{\rho_k}{\tau_k} \vec{u}' = \sum_k \frac{1}{\tau_k}\sum_i f_i^k\vec{c}_i
\end{equation}

This recasting of the velocity ensures that in the absence of forces, the total momentum of the system is conserved.

\section{Suspended particle dynamics}
\label{section:lbm_colloids}

Suspended particles will be coupled to the LB fluid based on the work conducted by Ladd. \cite{ladd_numerical_1994, 
aidun_direct_1998, ladd_lattice-boltzmann_2001} The particles follow Newtonian mechanics with the particle force and
rotational inertia defined using differential equations

\begin{equation}
    \begin{split}
    \vec{F_p} = m_p \frac{\vec{u}_p}{dt} , \\
    \vec{D_p} = \mathbf{J}_p \frac{\vec{\omega}_p}{dt} ,
    \label{eq:md}
    \end{split}
\end{equation}

$\mathbf{F_p}$ and $\mathbf{D_p}$ represent the force and torque acting on a particle with mass $m_p$ and moment of inertia 
$\mathbf{J}_p$. $\mathbf{u}_p$ and $\mathbf{\omega_{p}}$ are the linear and angular velocities of the particle. The equations of 
motion are evolved over time using a leapfrog integrator. \cite{jansen_bijels_2011}

The particles are discretized on the lattice according to the method laid out in Ladd and Aidun 
\cite{ladd_lattice-boltzmann_2001}. Nodes representing the particle are marked as solid nodes that replicate
a no-slip boundary condition through a moving bounce-back boundary. This is implemented into the distribution function
by reflecting the outgoing populations of $f_i^k$ to the opposite lattice velocity

\begin{equation}
    f^k_{i^\star}(\vec{x}, t+\Delta t) = f^{k,\star}_i(\vec{x}, t) - \frac{2w_i}{c_s^2} \rho \vec{u}_i \cdot \vec{c}_i ,
\end{equation}

This facilitates momentum exchange between particle and fluid which can be calculated analytically as 
\(\Delta\vec{p}^k_i \frac{\Delta t}{(\Delta x)^3} = 2 f^{k,\star}_i(\vec{x},t)\vec{c}_i - \frac{2w_i}{c_s^2}\rho(\vec{u}_i\cdot\vec{c}_i)\vec{c}_i\).
The sum of the momentum change across the surface of the particle is computed to obtain the force and torque on the particle,

\begin{equation}
    \begin{split}
    \vec{F}_p &= \sum_{k,i} \frac{\Delta \vec{p}^k_i}{\Delta t} , \\
    \vec{T}_p &= \sum_{k,i} \frac{\Delta\vec{p}^k_i}{\Delta t} \times \vec{r}_i .
    \end{split}
\end{equation}

As the particle moves, the nodes representing the particle are updated, with newly covered grid points marked as solid and 
uncovered nodes marked as fluid. When a grid point is covered, the momentum contained in that lattice point is added to the 
total force of the particle,

\begin{equation}
    \vec{F}_p = -\sum_{k,i} f_i^k(\vec{x},t)\vec{c}_i .
\end{equation}

Upon uncovering of a grid point, it is assigned a density value that represents the average of all adjacent fluid sites,

\begin{equation}
    \rho^k(\vec{x},t) = \frac{1}{N_{\text{f}}} \sum_{i_{\text{f}}} \rho^k(\vec{x}+\vec{c}_{i_{\text{f}}n}, t)
    \label{eq:fill_particles}
\end{equation}

\subsection{Anisotropic particles}
\label{section:lbm_colloids_ellipsoids}

For particles close to contact, meaning with inter-surface distances under 1 lattice unit the hydrodynamics are unresolved as the
distance is smaller than what the model can resolve. Lubrication forces are added to reduce the likelihood of particle overlap. For 
spherical particles, this is defined in Equation \ref{eq:sphere_lube}

\begin{equation}
    \vec{F}_l = -6 \pi \eta \frac{R_1^2 R_2^2}{\left(R_1+R_2\right)^2}\left(\frac{1}{|\vec{r}_{ij}|-R_1-R_2}-\frac{1}{d_c}\right) \frac{\left(\vec{u}_{12}\cdot\vec{r}_{12}\right)\vec{r}_{12}}{|\vec{r}_{12}|^2} ,% \qquad d<d_c,
    \label{eq:lubrication}
\end{equation}

where $R_i$ and $R_j$ are the radii of each particle involved in the interaction, $\vec{r}_{ij}$ is the distance
vector between the particle centers, $\mathbf{u}_{ij}$ are the relative velocities of the particles and $\Delta_c$ 
is the cutoff distance when the lubrication force begins to act. If particles are able to overcome the lubrication forces, 
a hertzian contact force is also added to ensure that there is no particle overlap, defined in Equation \ref{eq:hertz_def}

\begin{equation}
    \phi_{H} = K_{H}(R_i + R_j - |\mathbf{r}_{ij}|)^{5/2}, r < R_i + R_j
    \label{eq:hertz}
\end{equation}

$K_H$ is the force constant used to push particles apart. To correct for the anisotropic particles used in this work, 
the formulas presented in Eqs \ref{eq:lubrication} and \ref{eq:hertz} can be generalized using the route followed 
in Gunther et al. and Davies et al., inspired by Berne and Pechukas. \cite{gunther_timescales_2014, davies_interface_2014} 
They first begin by rewriting the lubrication and Hertzian contact forces as a function of the particle orientation and 
aspect ratio of the particles.

\begin{equation}
    \begin{split}
    \phi(\vec{r}_{ij}) &= {\epsilon} \tilde{\phi}\left(\frac{\vec{r}_{ij}}{{\sigma}}\right) , \\
    \vec{F}(\vec{r}_{ij}) &= {\epsilon} \tilde{\vec{F}}\left(\frac{\vec{r}_{ij}}{{\sigma}}\right) .
    \end{split}
\end{equation}

For the lubrication force \eqref{eq:lubrication}, we choose
${\sigma}=R_1+R_2$ and ${\epsilon}=\frac{6\pi\eta R_1^2 R_2^2}{{\sigma^3}}$, and for the
Hertz potential we chose ${\sigma}=R_1+R_2$ and ${\epsilon}=K_H\sigma^{5/2}$. For two identical, rotationally
symmetric ellipsoidal particles with orientations $\hat{\vec{o}}_i$ and $\hat{\vec{o}}_j$, we then replace $\epsilon$ and $\sigma$ by
the anisotropic functions

\begin{equation}
    \begin{split}
    \tilde\epsilon\left(\hat{\vec{o}}_i, \hat{\vec{o}}_j\right) &= \frac{{\epsilon}}{\sqrt{1-\chi^2}} , \\
    %\qquad \chi = \frac{\left(\alpha^2-1\right)R_\parallel^2}{\left(\alpha^2+1\right)R_\parallel^2}\left(\hat{\vec{o}}_i\hat{\vec{o}}_j\right) , \\
    \tilde\sigma\left(\vec{r}_{ij}, \hat{\vec{o}}_i, \hat{\vec{o}}_j\right) &= \frac{{\sigma}}{\sqrt{1-\frac{\chi}{2}\left[ \frac{\left(\hat{\vec{r}}_{ij}\cdot\hat{\vec{o}}_i+\hat{\vec{r}}_{ij}\cdot\hat{\vec{o}}_j\right)^2}{1+\chi\left(\hat{\vec{o}}_i\hat{\vec{o}}_j\right)} + \frac{\left(\hat{\vec{r}}_{ij}\cdot\hat{\vec{o}}_i-\hat{\vec{r}}_{ij}\cdot\hat{\vec{o}}_j\right)^2}{1-\chi\left(\hat{\vec{o}}_i\hat{\vec{o}}_j\right)} \right] }} , \\
    \chi &= \frac{\alpha^2-1}{\alpha^2+1} , \\
    \end{split}
\end{equation}

where $R_{\parallel}$ is the particle radius along the
symmetry axis $\hat{o}$ and $\alpha=\frac{R_{\parallel}}{R_{\perp}}$ the aspect
ratio of the particle. The anisotropic Hertz potential and lubrication
force are then defined as
%
\begin{equation}
    \begin{split}
    \phi\left(\vec{r}_{ij}, \hat{\vec{o}}_i, \hat{\vec{o}}_j\right) &= \epsilon\left(\hat{\vec{o}}_i, \hat{\vec{o}}_j\right) \tilde{\phi}\left(\frac{\vec{r}_{ij}}{\sigma\left(\vec{r}_{ij}, \hat{\vec{o}}_i, \hat{\vec{o}}_j\right)} \right) , \\
    \vec{F}\left(\vec{r}_{ij}, \hat{\vec{o}}_i, \hat{\vec{o}}_j\right) &= \epsilon\left(\hat{\vec{o}}_i, \hat{\vec{o}}_j\right) \tilde{\vec{F}}\left(\frac{\vec{r}_{ij}}{\sigma\left(\vec{r}_{ij}, \hat{\vec{o}}_i, \hat{\vec{o}}_j\right)} \right) .
    \end{split}
\end{equation}

\subsection{Magnetic field and particle coupling}
\label{section:lbm_colloids_magnetics}
